Technique for \earlywarning\ filtering for compact binary coalescence and its implications for multi-messenger astronomy

### 2011-06-29 introduction.tex
Removed some fluff in sentence listing sky localization uncertainties from Table 1
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@1189 ccdd05d5-56c1-461a-bf98-85f6876523b4

Before discussing realistic latencies, it is important to note that \EM{}
followup requires estimating the location of the \GW{} source. The localization
uncertainty is dominated by uncertainty in the time of arrival of the \GW{}s,
which is determined by the signal's effective bandwidth and \SNR{}
\citep{Fairhurst2009}.  Table~\ref{fig:earlywarning} and
Figure~\ref{fig:sky-localization-accuracy} show the estimated minimum 90\%
confidence area versus time of the loudest coalescence events detectable by
Advanced \LIGO{} and Advanced Virgo.  Once per year, we expect to observe an
event with a final \SNR\ of $\sim 27$ whose location can be constrained to about
1300\,deg$^2$ (3.1\% of the sky) using only the waveform 25\,s before merger,
260\,deg$^2$ (0.63\% of the sky) using the waveform 10\,s before merger, and
0.82\,deg$^2$ (0.0020\% of the sky) using the full \GW\ waveform.

>>>>

Before discussing realistic latencies, it is important to note that \EM{}
followup requires estimating the location of the \GW{} source. The localization
uncertainty is dominated by uncertainty in the time of arrival of the \GW{}s,
which is determined by the signal's effective bandwidth and \SNR{}
\citep{Fairhurst2009}.  Table~\ref{fig:earlywarning} and
Figure~\ref{fig:sky-localization-accuracy} show the estimated minimum 90\%
confidence area versus time of the loudest coalescence events detectable by
Advanced \LIGO{} and Advanced Virgo.  Once per year, we expect to observe an
event with a final \SNR\ of $\sim 27$ whose location can be constrained to about
1300\,deg$^2$ (3.1\% of the sky) within 25\,s of merger,
260\,deg$^2$ (0.63\% of the sky) within 10\,s of merger, and
0.82\,deg$^2$ (0.0020\% of the sky) at merger.
